Clustering: A pipeline to analyse time-course gene expression data

### 2019-05-02 scripts/03_clustering.Rmd
Implementing consensus strategy
Removing consensus method (takes too long)

```{r}
n_clusters = 5:20
all_labels = list()
for(i in n_clusters){
    filename = paste0("results/stability_", i, ".tsv")
    stability = read.table(filename, sep="\t")
    all_labels[[paste0("C", i)]] = stability
}
```

```{r fig.width=8, fig.height=8}
library(moanin)
moanin::plot_model_explorer(all_labels)
```

>>>>

```{r}
n_clusters = 2:20
all_labels = list()
for(i in n_clusters){
    filename = paste0("results/stability_", i, ".tsv")
    stability = read.table(filename, sep="\t")
    all_labels[[paste0("C", i)]] = stability
}
```

#### The model explorer strategy

```{r fig.width=8, fig.height=8}
moanin::plot_model_explorer(all_labels)
```

#### Looking at the CDF of the consensus matrix

```{r fig.width=8, fig.height=8}
#moanin::plot_cdf_consensus(all_labels)
```
